SoK: Transparent Dishonesty: front-running attacks on Blockchain.

### 2019-02-13 frontrunning/Latex/sections/paper.tex
[frontrunning] minor edit

%Shayan -> TODO: Jeremy: the following probably needs some rewrite to focus on the solution rather than the issue.
Another example in the design of ERC20 standard~\cite{erc20}, is on the allowance functionality. \textit{approve()} function in the specification allows a second entity to be able to spend N tokens from the sender's balance. In order to change the allowance, sender must send a transaction to set the new allowance value. Using the insertion attack, attacker could front-run the new allowance transaction and spend the old value before the new value is set~\cite{blockchainProjectAllowanceAttack,erc20GithubIssue}. Solutions such as \textit{decreaseApproval()}/\textit{increaseApproval()} were added in updated implementations.

>>>>

%Shayan -> TODO: Jeremy: the following probably needs some rewrite to focus on the solution rather than the issue.
Another example in the design of ERC20 standard~\cite{erc20}, is on the allowance functionality. \textit{approve()} function in the specification allows a second entity to be able to spend N tokens from the sender's balance. In order to change the allowance, sender must send a transaction to set the new allowance value. Using the insertion attack, attacker could front-run the new allowance transaction and spend the old value before the new value is set~\cite{blockchainProjectAllowanceAttack,erc20GithubIssue}, and then additionally spend the new amount at a later time. Solutions such as \textit{decreaseApproval()}/\textit{increaseApproval()} were added in updated implementations.
